ANIME

### 2024-02-25 paper.qmd
add integration formulae

## Integration of Attributes

@@

>>>>

## Integration of Numeric Attributes

@@

### Extensive Numeric Attribute Integration

sum of shared length / length of y *

let the shared length between target i and source j be the variable $SL_{ij}$

$$
\hat{Y}_i = \sum_{j} \frac{SL_{ij}}{length(j)} \times Y_j
$$

### Intensive Numeric Attribute Integration

$$
\hat{Y}_i = \text{mean}\left(\frac{SL_{ij}}{length(i)} \times Y_j\right)
$$

## Integration of Categorical Attributes

Similar to the the approach taken for numeric attributes, we can also apply these to categorical variables. Say we have a categorical variable $Y$ with $k$ unique values. For each $j$ we calculate a frequency table for each $Y_{jk}$. We create new variable for each unique $Y_k$. $Y_{ik}$ becomes a numeric variable of the frequency. $Y_{jk}$ is a dummy variable. We now apply the same approach for extensive and intensive attribute integration for each new dummy variable.

### Extensive Categorical Attribute Integration

$\hat{Y_{ik}}$ is equal to the shared length divided by the length of j times $Y_{jk}$ summed for all $ij$ pairs. Note that $Y_{jk}$ can take on only the values of 1 or 0.

$$
\hat{Y_{ik}} = \sum_{j}{\frac{SL_{ij}}{length(j)}} \times Y_{jk}
$$

### Intensive Categorical Attribute Integration

$$
\hat{Y_{ik}} = \text{mean}\left(\frac{SL_{ij}}{length(i)} \times Y_{jk}\right)
$$
